---
title: "Replication of Experiential or Material Purchase? Social Class Determines Purchase Happiness. Lee, Hall & Wood (2018, Psychological Science)"
author: "Elizabeth Mortenson (mortenson@stanford.edu)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: false
---

eval=FALSE

```{r}
####Load Relevant Libraries and Functions
install.packages("tidyverse")
library("tidyverse")
```

```{r}
###Import data
setwd('/Users/homefolder/Desktop/lee2018/original_data')

```



```{r}
#Creating subject ID row and removing unnecessary columns
lee2_orig <- lee_import %>% 
  select(ComparativeHappiness:MacArthurScale)
# mutate(subid = row_number())
   View(lee2_orig)
   
   lee2_orig %>% group_by(MacArthurScale) %>%summarise(mean_val = mean(ComparativeHappiness))
   
   #Question: Do we need a subject ID column specifically, or is there a way to use the first column as the IDs?
```

less than 30 data points don't have normal distribution


###Data Preparation
, eval=FALSE
```{r, eval=FALSE}
  
#Recoding IV and DV measures and renaming
 lee3 <- lee2 %>% 
 mutate(happy=recode(lee2$CompHap, 
                     `2` = -2, `3` = -3, 
                     `1` = -1, `-3` = 3, 
                     `-1` = 1, `-2` = 2)) %>% 
mutate(SES=recode(lee2$MacArthurSES, 
                  `1` = 10, `2` = 9, `3` = 8,
                  `4` = 7, `5` = 6, 
                  `6` = 5, `7` = 4, 
                  `8` = 3, `9` = 2, `10` = 1))
 View(lee3)

```

```{r, eval=FALSE}
 #Converting wide to long format  
d <- lee2_orig %>% 
 gather(Measures, Values, 1:10)
 View(d)

```


### Confirmatory analysis

*A little data visualization*
, eval=FALSE
```{r}
d %>%
ggplot(aes(x = lee2_orig$MacArthurScale, y = lee2_orig$ComparativeHappiness)) +
 geom_point(colour = "blue")

```

*Getting Pearson correlation*

, eval=FALSE
```{r}

cor(lee2_orig$ComparativeHappiness, lee2_orig$MacArthurScale)

```


*Plotting the model*
, eval=FALSE
```{r}

figure <- lee2_orig %>%
 ggplot(aes(x = MacArthurScale, y = ComparativeHappiness)) +
 geom_point(colour = "red") +
 geom_smooth(method = "lm", fill = NA)

figure + geom_hline(yintercept=0, color = "black") +
  geom_vline(xintercept = 0, color = "black") 
 # geom_vline(xintercept = XX, linetype="dashed", color = "blue") +
 # geom_vline(xintercept = XX, linetype="dashed", color = "blue")

  
```
r confidence interval linear regression fitted data
qt() = quantile distribution

fitted value = y hat is the outcome value predicted by the line--not the one we actually observed, they can be very different

it has predictive power even though the r is close to 0, b/c the p value is very small

residual standard error




*Side-by-side graph with original graph is ideal here*

###Exploratory analyses

Any follow-up analyses desired (not required).  

## Discussion

### Summary of Replication Attempt

Open the discussion section with a paragraph summarizing the primary result from the confirmatory analysis and the assessment of whether it replicated, partially replicated, or failed to replicate the original result.  

### Commentary

Add open-ended commentary (if any) reflecting (a) insights from follow-up exploratory analysis, (b) assessment of the meaning of the replication (or not) - e.g., for a failure to replicate, are the differences between original and present study ones that definitely, plausibly, or are unlikely to have been moderators of the result, and (c) discussion of any objections or challenges raised by the current and original authors about the replication attempt.  None of these need to be long.
